---
title: "Final project"
author: "Richard Smeltzer"
output: html_notebook
---

# Guided question
Was a 2019 MLB player's batting ability affected by his age? I will be taking a look at several different batting statistics compared to each player's age, to see if there was any correlation apparent between the two. 



# Getting acquainted with my data sources

## Where did you find them?
All of my data will be gathered from baseballreference.com. They have a way that allows you to copy and paste data as .csv, which will make importing it into R so much easier.

### Who collected/maintains them?
Baseball reference is run by several moderators at the site. They gather this either by watching games, or taking the data from other websites. Sports data is fairly well-kept on the internet.

## When and why were they originally collected?
They were originally collected because sports fans love to read and interpret statistics from each player. This specific data set I will be using was collected during the 2019 Major League Baseball season.

## What does a case represent in each data source, and how many total cases are available?
Each case is represented by an individual player. In the final version of my project, I will have players from all 30 MLB teams. For the time being however, I am just working with players from the Baltimore Orioles. For now, this data set has 58 cases.

## What are some of the variables that you plan to use?
I plan to look at player ages, hits, home runs, RBIs, stolen bases, on-base percentage, and OPS+



# Explore intuition relating to research question

## Reading libraries to use
```{r}
library(mosaic)
library(tidyverse)
library(mosaicData)
library(ggplot2)
library(DataComputing)
library(lubridate)
library(readr)
```

## Inputting data
```{r}
Orioles <-
  read_csv("Age,H,HR,RBI,SB,OBP,OPSplus
,,,,,,
25,76,13,44,3,.321,95
33,55,12,36,0,.276,60
28,176,24,73,40,.339,109
24,59,6,23,10,.260,54
25,86,12,46,0,.306,81
26,86,13,53,5,.297,86
27,74,10,35,3,.286,76
27,175,35,97,1,.364,135
25,132,31,90,1,.311,101
26,160,12,51,4,.329,98
24,99,20,59,1,.297,101
24,35,8,20,0,.333,94
25,30,4,15,1,.317,85
28,24,2,6,3,.304,74
29,21,4,9,4,.261,61
29,22,2,11,4,.269,59
23,21,4,13,2,.373,147
24,6,0,4,1,.181,-8
28,15,1,5,0,.247,39
31,13,0,3,0,.269,39
27,8,0,2,1,.324,69
33,5,0,3,0,.226,33
25,0,0,0,0,.250,-22
25,0,0,0,0,.000,-100
25,0,0,0,0,.000,-100
29,0,0,0,0,.000,-100
32,0,0,0,0,.000,-100
26,1,0,0,0,1.000,439
25,0,0,0,0,.000,-100
26,0,0,0,0,.000,-100
30,0,0,0,0,.000,-100
26,0,0,0,0,,
27,0,0,0,0,,
32,0,0,0,0,,
28,0,0,0,0,,
29,0,0,0,0,,
24,0,0,0,0,,
25,0,0,0,0,,
27,0,0,0,0,,
27,0,0,0,0,,
27,0,0,0,0,,
27,0,0,0,0,,
30,0,0,0,0,,
25,0,0,0,0,,
25,0,0,0,0,,
26,0,0,0,0,,
28,0,0,0,0,,
26,0,0,0,0,,
31,0,0,0,0,,
24,0,0,0,0,,
29,0,0,0,0,,
24,0,0,0,0,,
28,0,0,0,0,,
31,0,0,0,0,,
24,0,0,0,0,,
24,0,0,0,0,,
29,0,0,0,0,,
23,0,0,0,0,,")
```

## Making exploratory charts
### Age vs hits
```{r}
Orioles %>%
  ggplot(aes(x=Age, y=H)) +
  geom_point() + geom_smooth(method="lm")
```

### Age vs stolen bases
```{r}
Orioles %>%
  ggplot(aes(x=Age, y=SB)) +
  geom_point() + geom_smooth(method="lm")
```

### Age vs OPS+
```{r}
Orioles %>%
  ggplot(aes(x=Age, y=OPSplus)) +
  geom_point() + geom_smooth(method="lm")
```

## Description of preliminary findings
I only looked at three of the variables vs. Age so far. When looking at hits, the trend seems to follow a negative correlation. The graphs for stolen bases and OPS+ seem to follow flat lines, but this could change when working with the complete data set.



# Data sources (so far)

## Orioles
```{r}
View(Orioles)
```

## BlueJays
```{r}
BlueJays <-
  read_csv("Age,H,HR,RBI,SB,OBP,OPSplus
,,,,,,
24,72,13,43,0,.279,70
32,86,22,61,0,.342,101
24,83,16,48,14,.364,113
29,120,18,54,4,.299,96
20,126,15,69,0,.339,106
25,87,20,50,6,.327,127
26,96,26,65,6,.306,105
27,136,31,80,2,.280,93
24,84,21,54,1,.293,95
26,91,15,41,0,.262,70
33,86,10,30,6,.363,123
24,54,12,28,0,.274,83
21,61,11,21,4,.358,144
28,18,2,9,1,.205,18
25,15,6,12,1,.271,72
24,29,5,11,0,.346,130
27,15,2,6,3,.266,44
23,18,0,4,0,.273,60
26,7,0,4,1,.229,9
26,3,0,2,0,.163,-19
24,5,1,1,2,.233,39
30,1,0,1,0,.059,-67
27,4,1,3,0,.267,106
29,0,0,0,0,.000,-100
25,0,0,0,0,.333,4
25,2,0,0,0,.667,262
35,0,0,0,0,.000,-100
26,0,0,0,0,.000,-100
28,0,0,0,0,.000,-100
19,0,0,0,0,.000,-100
23,0,0,0,0,.000,-100
23,0,0,0,0,.000,-100
29,0,0,0,0,.000,-100
29,0,0,0,0,,
27,0,0,0,0,,
33,0,0,0,0,,
29,0,0,0,0,,
30,0,0,0,0,,
33,0,0,0,0,,
28,0,0,0,0,,
34,0,0,0,0,,
31,0,0,0,0,,
31,0,0,0,0,,
27,0,0,0,0,,
32,0,0,0,0,,
22,0,0,0,0,,
27,0,0,0,0,,
27,0,0,0,0,,
27,0,0,0,0,,
29,0,0,0,0,,
32,0,0,0,0,,
29,0,0,0,0,,
31,0,0,0,0,,
26,0,0,0,0,,
32,0,0,0,0,,
24,0,0,0,0,,
35,0,0,0,0,,
28,0,0,0,0,,
25,0,0,0,0,,
25,0,0,0,0,,
26,0,0,0,0,,")
```